Benchmarking on Rigetti architecture

### 2022-12-07 txt/manuscript.tex
Update abstract, keywords and authors

\title{Benchmarking on Rigetti architecture}

@@

\author{Paulina Lewandowska}
\author{\L ukasz Pawela}

@@

\begin{abstract}
We introduce library ?, a comprehensive open source framework for benchmarking 
Amazon Braket Rigetti IonQ architectures ? 
The framework is built around  the scheme of discrimination of von Neumann 
measurements. The library provides algorithm for ... Our main aim is creating a 
common platform  for open research.  ?

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Benchmarking of Rigetti architecture \sep Discrimination of quantum 
measurements \sep Von Neumann measurements discrimination

>>>>

\title{}

@@

\author{Konrad Jałowiecki}
\author{Paulina Lewandowska}
\author{Profesor Kierownik \L ukasz Pawela}

@@

\begin{abstract}
We introduce PyQBench, an innovative open-source framework for benchmarking 
gate-based quantum computers. PyQBench can benchmark NISQ devices by verifying their capability of
discriminating between two von Neumann measurements. PyQBench offers a simplified, ready-to-use,
command line interface (CLI) for running benchmarks using a predefined parametrized Fourier
family of measurements. For more advanced scenarios, PyQBench offers a way of employing user-defined
measurements instead of predefined ones.

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Quantum computing \sep
Benchmarking quantum computers \sep 
Discrimination of quantum measurements \sep 
Discrimination of von Neumann Measurements \sep
Open-source \sep
Python programming
